\huge Modeling Intervention Strategies for TB Control in the United States

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
Added economic modeling description to beamer poster

>>>>

      \begin{block}{Economic Modeling}
        We extended our basic implementation of the Hill model to incorporate
        economic data of treatment costs for Active and Latent Tuberculosis.  
        In our model, we estimate the average heath care costs to be \$14,014.90
        and \$403.45 to treat a single case of Active or Latent TB respectively.  
        Given these costs and the average treatment rates for Active and Latent
        TB in the USA, we modeled the expected economic burden of Tuberculosis
        projected over the next hundred years.        
